Reviewer comments from PeerJ

### 2015-03-02 PeerJResponse.tex
Edits
edits to text and response for Reviewer 2

\lev{Simply put it is what we had available at the time. There was no specific choosing or decision about number of individuals per accession}
\mbh{we'll have to diplomatically state this...we sampled all teosinte available to us and while this didn't allow for even sample sizes across populations, it did allow us to calculate both frequency in a subset of populations and geographic breadth of the \emph{Hopscotch} across a large number of independent sampling locations}

@@

\lev{Okay. Is there somewhere we can get all of this info.? I don't believe I have access to the database any more}
\mbh{Yes, we need to include this info.; that's a fair request}
\lev{Do either of you know where I can find this info?}

@@

\lev{Why what? Why two products? or why did we do it that way? I think it is clearly stated that we can test for presence/absence/hets and pcr bias with sometimes a large fragment being difficult to amplify. The location of the primers is all shown in the cartoon figure and stated in the text. two primers outside of LTR one primer within.}

\mbh{if there's any way to be even slightly more clear, I'd edit just so you can say here that you've edited for clarity}

@@

\lev{What? It is in the LTR!!!! Gah! That's the whole point!}

>>>>

\res{We sampled all individuals and populations that were available to us, which while it did not allow for even sample sizes across populations, did allow us to calculate \emph{Hopscotch} frequency in a subset of populations, as well as the geographic distribution of the \emph{Hopscotch} across many independent sampling locations. We have added a clarifying statement to the text regarding our sampling: page 4, lines 63-68: ``We sampled all individuals and populations that were available to us, consisting of 1,110 individuals from 350 \track{populations} (247 maize landraces, 17 \emph{mexicana} populations, and 86 \emph{parviglumis} populations) and assessed the presence or absence of the \emph{Hopscotch} insertion (Table S1 and Table S2, See Supplemental Materials with the online version of this article). Numbers of individuals sampled \track{per population} ranged from 1-43 for \emph{parviglumis}, 1-35 for \emph{mexicana}, and 1-18 for the maize landrace populations. Available samples did not allow us to sample evenly from populations, but did allow us to calculate \emph{Hopscotch} frequency in a subset of populations, as well as elucidate the geographic distribution of the \emph{Hopscotch} across multiple independent sampling sites."}

@@

\lev{I don't have access to this info. Can one of you guys help?}

@@

\res{There are three primers that make up the two primer sets used to genotype individuals for the \emph{Hopscotch} element. The primers are HopF, located upstream of the element; IntHopR, located within the LTR; and HopR, located downstream of the element. HopF and HopR are used as one reaction, resulting in either a 5kb product (the whole element) or a small band ~300bp (sequence on eitheir end of the element). HopF and IntHopR are used to amplify a portion of th element (~1.1kb). Smaller bands preferentially amplify over larger bands when in the same reaction, so we chose to add the HopF/IntHopR PCR reaction as a way to get around PCR bias when amplifying both a larger (5kb) and smaller (300bp) band at the same time during the HopF/HopR reaction. A plant homozygous for the \emph{Hopscotch} insertion will produce one 5kb band in the HopF/HopR reaction and one 1.1kb band in the HopF/HopIntR reaction. A heterozygous individuals will have two bands for the HopF/HopR reaction (one 5kb and one 300bp) as well as a 1.1kb band for the HopF/HopIntRR reaction, totaling 3 bands. The two reactions were run in separate wells on an agarose gel to allow for scoring.}

\res{We have added some clarifying text to the manuscript: page 4, lines 75-86: ``Two PCRs were performed for each individual, one with primers flanking the \emph{Hopscotch} (HopF/HopR) and one with a flanking primer (HopF) and an internal primer (HopIntR). Primer sequences are HopF, {\small 5'-TCGTTGATGCTTTGATGGATGG-3'}; 
HopR, {\small 5'-AACAGTATGATTTCATGGGACCG-3'}; and HopIntR, {\small  5'-CCTCCACCTCTCATGAGATCC-3'} (Fig. S1 and \track{\ref{Fig1Cartoon}}, See Supplemental Materials with the online version of this article). Homozygotes for the no-\emph{Hopscotch} allele show a single band for absence of the element ($\sim$300bp) produced by the HopF/HopR primer set, and 0 bands for the HopF/HopIntR primer set since they lack the LTR where the internal primer sequence is. Homozygotes for the \emph{Hopscotch} allele also show one band at 5kb for the HopF/HopR PCR product as well as one band at 1.1kb for the HopF/HopIntR PCR. Heterozygotes for the \emph{Hopscotch} allele show three bands total; both a 300bp band and a 5kb band for the HopF/HopR PCR and a 1.1Kb band for the HopF/HopIntR PCR (Table S2, See Supplemental Materials with the online version of this article)."}

@@

\res{The HopIntR primer is within the LTR element and was designed off of previously sequence data provided by John Doebley.}

### 2015-03-02 PeerJ_trackchanges.tex
Edits
edits to text and response for Reviewer 2

\textbf{Sampling and genotyping---}We sampled 1,110 individuals from 350 \track{populations} (247 maize landraces, 17 \emph{mexicana} populations, and 86 \emph{parviglumis} populations) and assessed the presence or absence of the \emph{Hopscotch} insertion (Table S1 and Table S2, See Supplemental Materials with the online version of this article). Numbers of individuals sampled \track{per population} ranged from 1-43 for \emph{parviglumis}, 1-35 for \emph{mexicana}, and 1-18 for the maize landrace populations. DNA was extracted from leaf tissue using a modified CTAB approach \citep{DoyleDoyle1990, Maloof1984}. We designed primers using PRIMER3 \citep{RozenSkaletsky2000} implemented in Geneious \citep{Kearse2012} to amplify the entire \emph{Hopscotch} element, as well as an internal primer allowing us to simultaneously check for possible PCR bias between presence and absence of the \emph{Hopscotch} insertion due to its large size ($\sim$5kb). Two PCRs were performed for each individual, one with primers flanking the \emph{Hopscotch} (HopF/HopR) and one with a flanking primer and an internal primer (HopF/HopIntR). Primer sequences are HopF, {\small 5'-TCGTTGATGCTTTGATGGATGG-3'}; 
HopR, {\small 5'-AACAGTATGATTTCATGGGACCG-3'}; and HopIntR, {\small  5'-CCTCCACCTCTCATGAGATCC-3'} (Fig. S1 and \track{\ref{Fig1Cartoon}}, See Supplemental Materials with the online version of this article). Homozygotes show a single band for absence of the element ($\sim$300bp) and two bands for presence of the element ($\sim$5kb, amplification of the entire element, and $\sim$1.1kb, amplification of part of the element), whereas heterozygotes show all three bands (Table S2, See Supplemental Materials with the online version of this article). Since we developed a PCR protocol for each allele, if only one PCR resolved well, we scored one allele for that individual rather than infer the diploid genotype. We used Phusion High Fidelity Enzyme (Thermo Fisher Scientific Inc., Waltham, Massachusetts, USA) and the following conditions for amplifications: 98$^{\circ}$C for 3 min, 30 cycles of 98$^{\circ}$C for 15 s, 65$^{\circ}$C for 30 s, and 72$^{\circ}$C for 3 min 30 s, with a final extension of 72$^{\circ}$C for 10 min. PCR products were visualized on a 1\% agarose gel and scored for presence/absence of the \emph{Hopscotch} based on band size.

>>>>

\textbf{Sampling and genotyping---}\track{We sampled all individuals and populations that were available to us, consisting of 1,110 individuals from 350 \track{populations} (247 maize landraces, 17 \emph{mexicana} populations, and 86 \emph{parviglumis} populations) and assessed the presence or absence of the \emph{Hopscotch} insertion (Table S1 and Table S2, See Supplemental Materials with the online version of this article). Numbers of individuals sampled \track{per population} ranged from 1-43 for \emph{parviglumis}, 1-35 for \emph{mexicana}, and 1-18 for the maize landrace populations. Available samples did not allow us to sample evenly from populations, but did allow us to calculate \emph{Hopscotch} frequency in a subset of populations, as well as elucidate the geographic distribution of the \emph{Hopscotch} across multiple independent sampling sites.} DNA was extracted from leaf tissue using a modified CTAB approach \citep{DoyleDoyle1990, Maloof1984}. We designed primers using PRIMER3 \citep{RozenSkaletsky2000} implemented in Geneious \citep{Kearse2012} to amplify the entire \emph{Hopscotch} element, as well as an internal primer allowing us to simultaneously check for possible PCR bias between presence and absence of the \emph{Hopscotch} insertion due to its large size ($\sim$5kb). \track{Two PCRs were performed for each individual, one with primers flanking the \emph{Hopscotch} (HopF/HopR) and one with a flanking primer (HopF) and an internal primer (HopIntR). Primer sequences are HopF, {\small 5'-TCGTTGATGCTTTGATGGATGG-3'}; 
HopR, {\small 5'-AACAGTATGATTTCATGGGACCG-3'}; and HopIntR, {\small  5'-CCTCCACCTCTCATGAGATCC-3'} (Fig. S1 and \track{\ref{Fig1Cartoon}}, See Supplemental Materials with the online version of this article). Homozygotes for the no-\emph{Hopscotch} allele show a single band for absence of the element ($\sim$300bp) produced by the HopF/HopR primer set, and 0 bands for the HopF/HopIntR primer set since they lack the LTR where the internal primer sequence is. Homozygotes for the \emph{Hopscotch} allele also show one band at 5kb for the HopF/HopR PCR product as well as one band at 1.1kb for the HopF/HopIntR PCR. Heterozygotes for the \emph{Hopscotch} allele show three bands total; both a 300bp band and a 5kb band for the HopF/HopR PCR and a 1.1Kb band for the HopF/HopIntR PCR (Table S2, See Supplemental Materials with the online version of this article).} Since we developed a PCR protocol for each allele, if only one PCR resolved well, we scored one allele for that individual rather than infer the diploid genotype. We used Phusion High Fidelity Enzyme (Thermo Fisher Scientific Inc., Waltham, Massachusetts, USA) and the following conditions for amplifications: 98$^{\circ}$C for 3 min, 30 cycles of 98$^{\circ}$C for 15 s, 65$^{\circ}$C for 30 s, and 72$^{\circ}$C for 3 min 30 s, with a final extension of 72$^{\circ}$C for 10 min. PCR products were visualized on a 1\% agarose gel and scored for presence/absence of the \emph{Hopscotch} based on band size.
